The importance of alternatives in scalar implicature

### 2016-01-21 Paper/Paper.tex
minor tweaks before sharing with mike 1.12

\begin{abstract}
Succesful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, listeners routinely enrich the meaning of
``some'' to ``some, but not all'' when interpreting a sentence such as
``Bob ate some of the cookies.'' A Gricean account of this phenomena
assumes the presence of \emph{salient alternatives} with varying degrees
of informativity. ``Some,'' in the example above, is enriched to ``some,
but not all'' in the presence of the stronger alternative ``all.''
Empirical evidence for the presence of such alternatives and accounts of
their effect on implicature has been limited. Our current work explores
the role different scale representations may play in scalar implicature
using emperical measures of literal semantics and a Bayesian model of
implicature generation. Comparisons with human judgments indicate that
pragmatic inference may rely on fairly complete alternative sets rather
than the typical entialment only scales assumed in most research to
date.

@@

Successful communication regularly requires listeners to make inferences
that go beyond the literal semantic content of a speaker's utterance.
``Scalar implicature'' is a hallmark of such pragmatic enrichment. For
example, listeners routinely enrich the meaning of the scalar item
``some'' to ``some, but not all'' in sentences like ``Bob ate some of
the cookies'' (van Tiel, 2014). A Gricean account of this phenomena
assumes listeners reason about the intended meaning of a speaker while
incorporating knowledge about a) alternative scalar items a speaker
could have used (such as ``all'') and b) the relative informativity of
using such alternatives (Grice, 1975). Under the Gricean account, a
listener will infer that the speaker must have intended that Bob did not
eat ``all'' the cookies because it would have been
\emph{underinformative} for the speaker to use ``some'' when ``all''
could have been used.

The presence of ``salient" alternatives is critical to the standard
Gricean account of scalar implicature (Grice, 1975). Recent experimental
evidence appears to support this. Using a gumball paradigm, Degen \&
Tanenhaus (2014) demonstrated that the scalar item \emph{some} was
judged less appropriate (natural) for small sets of items when exact
numbers were seen as viable alternatives. This finding points to the
impact a particular alternative set can have on judgments regarding
scalar appropriateness. Using a fundamentally differnt approach, Franke
(2014) formalized the Gricean account of implicature using a Bayesian
model, modeling graded typicality judgments and scalar implicature.
Results supported `none', `one' and `all' as the most serious (salient)
alternatives to ``some.''

Taken together, each of the previous studies signal the importance of
scale representation (set of available alternatives) in scalar
implicature. However, like many recent investigations which have focused
only on a small subset of scalar items, both Degen \& Tanehaus (2014)
and Franke (2014) focus exclusively on the scalar family ``some/all.''
This lack ``Scalar Diversity'' (van Tiel, 2014) makes generalization
across different scalar families problematic. van Tiel (2014), found
substantial variation in the rate of upper-bounded construals among over
40 different scalar pairs. This finding suggests that implicature may
differ widely between different scales. We adopt a ``Scalar Diversity''
approach in our experimental design in order to extend our investigation
beyond ``some/all'' scalar items. In the following set of studies we
examine implicature for ``some/all'' and five additional scalar families
from a range of grammatical classes (see Figure 5 for a complete set of
scalar items used). The set of scalar items for this study were chosen
from among the 40 used in van Tiel (2014).

Consider a scalar item other than ``some'' - in the context of a scalar
item such as ``good'', the idea of set of lexical alternatives certainly
xfeels intuitive (``bad'', ``excellent'', etc.). But measuring the
extent to which these alternatives are salient is not so clear. Nor is
how to measure their impact on pragmatic intepretations of the scalar
item ``good.'' In an experimental setting, querying a participant about
the saliency of a particular alternative is problematic because the
alternative must be made salient during the query. In the spirit of
Franke (2014) and Degen \& Tanenhaus (2014), we pair a computational
model of implicature with empirical measurments of linguistic material.
This combination allows us to simulate the effect of various scale
representations on implicature. In particular, we adopt a Bayesian model
of implicature and a food-review paradigm to empirically quantify
literal semantics and pragmatic judgments for our scalar stimuli.

Bayesian models of pragmatic enrichment have accurately predicted human
judgments in ad-hoc (Frank \& Goodman, 2012) and embedded (Stulhumuller
\& Goodman, 2014) implicature settings. Our current model follows both
these studies and is based on Rational Speech-act theory (RSA). RSA
frames language understanding as a special case of social cognition
(Stulhumuller \& Goodman, 2014), in which listeners and speakers reason
about one-another. In this framework, a listener uses Bayesiain
inference to interpret the intended meaning \(m\) of a speaker who has
made an utterance \(u\). We will make the model specifications explicit
later in the paper.

In the following study we investigate the role of scale representation
on scalar implicature. To do so we combine a computational framework
with empirical measurements to simulate the type of scale
representations that might be available to a listener. In the following
sections we outline the specifics of the model and the particular
components for which we need to to make empirical measurements. We then
outline a series of experiments meant to a) quantify literal semantics
for otherwise ambiguous scalar items, b) measure pragmatic judgments and
c) generate a set of plausible alternatives for our set of scalar pairs
taken from van Tiel (2014). In particular, we adopt a food review
paradigm throughout our empirical data gathering, quantifying linguistic
meaning (both literal semantics and pragmatic judgments) as
distributions over star ratings. Finally, we simulate the impact of
three different scale representations, ``entailment'', ``mid'' and
``symmetric'' on implicature generation, comparing model predictions
with pragmatic judgments captured empirically. Results indicate that
humans may employ more ``fully specified'' scale representatinos,
relying on the presence of multiple alternatives during pragmatic
enrichment.

@@

\(\mathbf{p(u | m)}\) quantifies the \textbf{likelihood} that a speaker
would make a particular utterance \(u\) given an intended meaning \(m\).
Our model assumes that speakers choose words to maximize the utility of
an utterance in context. Utility is operationalized as the informativity
of a particular utterance (suprisal) minus a cost. In particular, the
speaker chooses an utterance in order to maximize the utility of a
listener who interprets her utterance literally \(p_{L0}(m|u)\). \(L_0\)
denotes a literal listener interpretation.
\[p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}\]

The \textbf{posterior} \(\mathbf{p_{L1}(m | u)}\) quantifies a
listener's pragmatic enrichment of an utterance \(u\) as degree of
belief that \(m\) is the intended meaning of the speaker, given an
utterance \(u\). \(L_1\) denotes a pragmatic listener interpration.

\subsection{Populating the model: Measuring literal semantics and
pragmatic
judgments}\label{populating-the-model-measuring-literal-semantics-and-pragmatic-judgments}

In order to simulate the role of scale representation on implicature we
pair a computational framework with empirical data. In particular we use
experimental tools to populate three components of the model. First, to
measure otherwise ambigous literal semantics \(\mathbf{p_{L0}(m|u)}\)
(our ``Scalar Diversity''" approach). Second, to generate a set of
plausible alternatives to the original scalar pairs taken from van Tiel
(2014). Lastly, to obtain human pragmatic judgments for model comparison
\(\mathbf{p_{L1}(m|u)}\).

@@

\[\text{\textit{some of the A's are B's.}}\]
\[[[some]] = \{<A, B> : |A \cap B| \geq 1 \}\]

\[\text{\textit{all of the A's are B's.}}\]
\[[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}\]

@@

In the following set of studies we adopt a food-review paradigm to
measure literal semantics and pragmatic judgments empirically. In order
to capture graded typicality judgments as in Degen \& Tanenhaus (2014)
we use a compatiblity measure dependent variable, pairing scalar items
with star-ratings in our literal listener task (Experiments 1a, 3a and
4). Data from these experiments is used to approximate the literal
listener semantics for a given scalar item \(u\) as a distribution over
star-ratings \(m \in \text{\{1 - 5 stars\}}\). Similarly, pragmatic
judgment data from Experiments 1b and 3b serve as our primary points of
comparison with model predictions \(\mathbf{p_{L1}(m|u)}\), again
quantifying judgments as distributions over star-ratings. In the
following section we take the read through our experiments.

@@

Experiment 1a and 1b were conducted to approximate literal listener
semantic distributions \(p_{L0}(m|u)\) (Exerpiment 1a) and pragmatic
judgments \(p_{L1}(m|u)\) (Experiment 1b) for five pairs of scalar items
taken from van Tiel (2014) (see figure 5 for stimuli). Each pair
consists of a ``weaker'' scalar term (e.g. ``some'') and a stronger
scalar term (e.g. ``all''). We are calling these ``entialment
scales''``, because they encode the assumption that a listener need only
have a the stronger alternative present to generate an enriched
interpretation of the weaker term. The grey colored items in Table 1
denote the original''entailment" items used in Experiments 1a,b.

@@

Participants for both tasks were recruited on Amazon Mechanical Turk and
paid \$0.20 for their participation. Thirty participants were recruited
for Experiment 1a. Data for two participants was thrown out during
analysis because there were not native English speakers, leaving a total
sample of 28 participants. Fifty participants were recruited for
experiment 1b. Data for 7 participants was thrown out after participants
either failed to pass two training trials or were not native English
speakers, leaving a total sample of 43 participants.

@@

Figure 2 plots literal listner \(p_{L0}(m|u)\) distributions obtained in
Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
variation between semantic judgments between scalar families in all the
Experiments. For example, compatibility judgments for ``memorable'' and
``forgettable'' are more similar than those for ``good / excellent'' or
``liked / loved''. We will address distributional similarity across the
studies in later sections.

@@

To test whether pragmatic judgments differed between Experiments 1b and
3b we ran a mixed effects model, regressing star-rating selections on
scale, scalar item and Exerpiment with random effects by subject.
Results indicate.

While conducting our analysis we realized that our literal semantic
distributions for each scalar family was roughly split between two
negative valenced items and two positively valenced items while more
neutral alternatives appeared to be left out. (This pattern was true of
all the scalar families, except for ``some ~all'' in which the top two
alternatives were positive valenced ``most'' and negative valenced
``none''.) In Experiment 4 we explore the addition of a neutrally
valenced scalar alternative for each scalar family.

\section{Experiment 4: Symmetric
scales}\label{experiment-4-symmetric-scales}

In Experiment 4, we continue to extend the alternative sets, each by one
additional scalar item. While we simply took the top two alternatives
generated in Experiment 2 for the additional alternatives in Experiments
3a,b, in this case we chose a subjectively ``neutral'' valenced scalar
item from among the alternatives generated in Experiment 2. The idea was
to simulate a ``full'' set of alternatievs with negative, neutral and
positive valenced items. The purple colored items in Table 1 denote
additional scalar items added in Experiments 4.

@@

Distributions for neturally valenced scalar did appear fairly gaussian,
occupying a literal semantic previously unoccupied by the other
alternatives.

@@

Using literal semantic data from Experiments 1a, 3a and 4 we conducted
three simulations with our model. Each simulation used the specific
literal semantic data to specify the scale representation avaiable to
our model. The ``entailment'' model used only the original pair of
scalar items pulled from van Tiel (2014). These data were measured in
Experiment 1a. The ``mid'' model used the extended the original set of
alternatives with the top two alternatives generated in Experiment 2.
These data were measured in Exerpiment 3a. The ``full'' model included
the full set of alternatives, including a neutral valenced alternatives.
These data were measured in Experiment 4.

@@

use a food review paradigm in which `meaning' for a given scalar item
was quantified as a distribution over star-ratings. Quantifying both
literal semantic content and pragmatic judgments as distributions over
stars provides an important interface to our model, especially for
scalar items with ambigous literal semantics (e.g.~items such as
``liked/loved'' or ``memorable/unforgettable''). In addition to
quantifying literal semantics and pragmatic judgments in Experiments
1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task,
based on van Tiel (2013, Experiment 2???), to generate a set of
plausible alternatives to the scalar items used in Experiments 1a,b. We
extend the set of alternatives measured in Experiments 3a,b and 4 using
data from Experimeng 2. Additionally, by looking at the relative
frequencies of alternatives generated in Experiment 2 we were able to
compute a saliency measure for each alternative. Using the literal
semantic data from Experiments 1a, 3a and 4, we modeled pragmatic
enrichment using RSA and compared model predictions to human judgments
obtained in Experiments 1b and 3b. Model performance was significantly
improved with the incorporation of alternatives. This result suggests
that more ``fully specified" scale representations may be active for
human participants while making pragmatic judgments for scalar items.

>>>>

\begin{abstract}
Succesful communication regularly requires listeners to make pragmatic
inferences - enrichments beyond the literal meaning of a speaker's
utterance. For example, listeners routinely enrich the meaning of
``some'' to ``some, but not all'' when interpreting a sentence such as
``Bob ate some of the cookies.'' A Gricean account of this phenomena
assumes the presence of \emph{salient alternatives} with varying degrees
of informativity. ``Some,'' in the example above, is enriched to ``some,
but not all'' in the presence of the stronger alternative ``all.''
Empirical evidence for the presence of such alternatives and accounts of
their effect on implicature has been limited. Our current work explores
the role different scale representations may play in scalar implicature
using empirical measures of literal semantics and a Bayesian model of
implicature generation. Comparisons with human judgments indicate that
pragmatic inference may rely on fairly complete alternative sets rather
than the typical entialment only scales assumed in most research to
date.

@@

Successful communication regularly requires listeners to make inferences
that go beyond the literal semantic content of a speaker's utterance.
``Scalar implicature'' is a hallmark of such pragmatic enrichment. For
example, listeners routinely enrich the meaning of the scalar item
``some'' to ``some, but not all'' in sentences like ``Bob ate some of
the cookies'' (van Tiel, 2014; other\ldots{}). A Gricean account of this
phenomena assumes listeners reason about the intended meaning of a
speaker while incorporating knowledge about a) alternative scalar items
a speaker could have used (such as ``all'') and b) the relative
informativity of using such alternatives (Grice, 1975). Under the
Gricean account, a listener will infer that the speaker must have
intended that Bob did not eat ``all'' the cookies because it would have
been \emph{underinformative} for the speaker to use ``some'' when
``all'' could have been used.

The presence of ``salient" alternatives is critical to the standard
Gricean account of scalar implicature (Grice, 1975). Recent experimental
evidence appears to support this. Using a gumball paradigm, Degen \&
Tanenhaus (2014) demonstrated that the scalar item \emph{some} was
judged less appropriate (natural) for small sets of items when exact
numbers were seen as viable alternatives. This finding points to the
impact a particular alternative set can have on judgments regarding
scalar appropriateness. Using a fundamentally different approach, Franke
(2014) formalized the Gricean account of implicature using a Bayesian
model, modeling graded typicality judgments and scalar implicature.
Results supported `none', `one' and `all' as the most serious (salient)
alternatives to ``some.''

Taken together, each of the previous studies signal the importance of
scale representation (set of available alternatives) in scalar
implicature. However, like many recent investigations which have focused
only on a small subset of scalar items, both Degen \& Tanenhaus (2014)
and Franke (2014) focus exclusively on the scalar family ``some/all.''
This lack ``Scalar Diversity'' (van Tiel, 2014) makes generalization
across different scalar families problematic. van Tiel (2014), found
substantial variation in the rate of upper-bounded construals aross more
than 40 different scalar pairs. This finding suggests that implicature
may differ widely between different scales. We adopt a ``Scalar
Diversity'' approach in our experimental design in order to extend our
investigation beyond ``some/all'' scalar items. In the following set of
studies we examine implicature for ``some/all'' and five additional
scalar families from a range of grammatical classes (see Figure 5 for a
complete set of scalar items used). The set of scalar items for this
study were chosen from among the 40 used in van Tiel (2014).

Consider a scalar item other than ``some'' - in the context of the word
``good'', the idea of set of lexical alternatives seems intuitive
(``bad'', ``excellent'', etc.). But measuring the extent to which these
alternatives are salient is not so clear. Nor is how to measure their
impact on pragmatic interpretations of the scalar item ``good.'' In an
experimental setting, querying a participant about the saliency of a
particular alternative is problematic because the alternative must be
made salient during the query. In the spirit of Franke (2014) and Degen
\& Tanenhaus (2014), we pair a computational model of implicature with
empirical measurements of linguistic material. This combination allows
us to simulate the effect of various scale representations on
implicature. In particular, we adopt a Bayesian model of implicature and
a food-review paradigm to empirically quantify literal semantics and
pragmatic judgments for our scalar stimuli.

Bayesian models of pragmatic enrichment have accurately predicted human
judgments in ad-hoc (Frank \& Goodman, 2012) and embedded (Stulhmuller
\& Goodman, 2014) implicature settings. Our current model follows both
these studies and is based on Rational Speech-act theory (RSA). RSA
frames language understanding as a special case of social cognition
(Frank \& Goodman, 2012; Stulhmuller \& Goodman, 2014), in which
listeners and speakers reason about one-another. In this framework, a
listener uses Bayesian inference to interpret the intended meaning \(m\)
of a speaker who has made an utterance \(u\). We will make the model
specifications explicit later in the paper.

In the following study we investigate the role of scale representation
on scalar implicature. To do so we combine a computational framework
with empirical measurements to simulate the type of scale
representations that might be available to a listener. In the following
sections we outline the specifics of the model and the particular
components for which we need to to make empirical measurements. We then
outline a series of experiments meant to a) quantify literal semantics
for otherwise ambiguous scalar items, b) measure pragmatic judgments and
c) generate a set of plausible alternatives for our set of scalar pairs
taken from van Tiel (2014). In particular, we adopt a food review
paradigm throughout our empirical data gathering, quantifying linguistic
meaning (both literal semantics and pragmatic judgments) as
distributions over star ratings. Finally, we simulate the impact of
three different scale representations, ``entailment'', ``mid'' and
``symmetric'' on implicature generation, comparing model predictions
with pragmatic judgments captured empirically. Results indicate that
humans may employ more ``fully specified'' scale representations,
relying on the presence of multiple alternatives during pragmatic
enrichment.

@@

\(\mathbf{p(u | m)}\) quantifies the \textbf{likelihood} that a speaker
would make a particular utterance \(u\) given an intended meaning \(m\).
Our model assumes that speakers choose words to maximize the utility of
an utterance in context. Utility is operationalized as the informativity
of a particular utterance (surprisal) minus a cost. In particular, the
speaker chooses an utterance in order to maximize the utility of a
listener who interprets her utterance literally \(p_{L0}(m|u)\). \(L_0\)
denotes a literal listener interpretation of meaning \(m\) given
utterance \(u\).
\[p(u | m) = \frac{e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}{\sum_{m \in M}e^{-\alpha(-log(p_{L0}(m|u)) - cost(u))}}\]

The \textbf{posterior} \(\mathbf{p_{L1}(m | u)}\) quantifies a
listener's degree of belief that a speaker intended a meaning \(m\)
given an utterance \(u\). The subscript \(L_1\) denotes a pragmatic
listener interpretation of meaning \(m\) given utterance \(u\).

\subsection{Simluating implicature: Measuring literal semantics and
pragmatic
judgments}\label{simluating-implicature-measuring-literal-semantics-and-pragmatic-judgments}

In order to simulate the role of scale representation on implicature we
pair a computational framework with empirical data. In particular we use
experimental tools to populate three components of the model. First, to
measure otherwise ambiguous literal semantics \(\mathbf{p_{L0}(m|u)}\)
(our ``Scalar Diversity''" approach). Second, to generate a set of
plausible alternatives to the original scalar pairs taken from van Tiel
(2014). Lastly, to obtain human pragmatic judgments for model comparison
\(\mathbf{p_{L1}(m|u)}\).

@@

\[\text{\text it{some of the A's are B's.}}\]
\[[[some]] = \{<A, B> : |A \cap B| \geq 1 \}\]

\[\text{\text it{all of the A's are B's.}}\]
\[[[all]] = \{<A, B> : \frac{|A \cap B|}{|A|} == 1 \}\]

@@

In the following set of studies we adopt a food-review paradigm to
measure literal semantics and pragmatic judgments empirically. In order
to capture graded typicality judgments as in Degen \& Tanenhaus (2014)
we use a compatibility measure dependent variable, pairing scalar items
with star-ratings in our literal listener task (Experiments 1a, 3a and
4). Data from these experiments is used to approximate the literal
listener semantics for a given scalar item \(u\) as a distribution over
star-ratings \(m \in \text{\{1 - 5 stars\}}\). Similarly, pragmatic
judgment data from Experiments 1b and 3b serve as our primary points of
comparison with model predictions \(\mathbf{p_{L1}(m|u)}\), again
quantifying judgments as distributions over star-ratings. In the
following section we take the reader through our experiments.

@@

Experiment 1a and 1b were conducted to approximate literal listener
semantic distributions \(p_{L0}(m|u)\) (Experiment 1a) and pragmatic
judgments \(p_{L1}(m|u)\) (Experiment 1b) for five pairs of scalar items
taken from van Tiel (2014) (see figure 5 for stimuli). Each pair
consists of a ``weaker'' scalar term (e.g. ``some'') and a stronger
scalar term (e.g. ``all''). We are calling these ``entailment scales'',
because they encode the assumption that a listener need only have a the
stronger alternative present to generate an enriched interpretation of
the weaker term. The grey colored items in Table 1 denote the original
``entailment'' items used in Experiments 1a,b.

@@

Participants for both tasks were recruited on Amazon Mechanical Turk and
paid \$0.20 for their participation. Thirty participants were recruited
for Experiment 1a. Data for two participants was thrown out during
analysis because they were not native English speakers, leaving a total
sample of 28 participants. Fifty participants were recruited for
Experiment 1b. Data for 7 participants was thrown out after participants
either failed to pass two training trials or were not native English
speakers, leaving a total sample of 43 participants.

@@

Figure 2 plots literal listener \(p_{L0}(m|u)\) distributions obtained
in Experiments 1a, 3a and 4. Data from 1a is (\ldots{}). We see clear
variation in semantic judgments between scalar families in all
Experiments. For example, compatibility judgments for ``memorable'' and
``forgettable'' are more similar than those for ``good / excellent'' or
``liked / loved''. We will address distributional similarity across the
studies in later sections.

@@

To test whether pragmatic judgments differed between Experiments 1b and
3b we ran a mixed effects model, regressing star-rating selections on
scale, scalar item and Experiment with random effects by subject.
Results indicate.

While conducting our analysis we realized that our literal semantic
distributions for each scalar family were roughly split between two
negative valenced items and two positively valenced items while neutral
alternatives appeared to be excluded. (This pattern was true of all the
scalar families, except for ``some ~all'' in which the top two
alternatives were positive valenced ``most'' and negative valenced
``none''.) In Experiment 4, we explore the addition of a neutrally
valenced scalar alternative for each scalar family.

\section{Experiment 4: Full scales - adding a neutral
alternative}\label{experiment-4-full-scales---adding-a-neutral-alternative}

In Experiment 4, we continue to extend the alternative sets, each by one
additional scalar item. While we simply took the top two alternatives
generated in Experiment 2 for the additional alternatives in Experiments
3a,b, in this case we chose a subjectively ``neutral'' valenced scalar
item from among the alternatives generated in Experiment 2. The idea was
to simulate a ``full'' set of alternatives, with negative, neutral and
positive valenced items for each scalar family. The purple colored items
in Table 1 denote additional scalar items added in Experiments 4.

@@

Distributions for neutrally valenced scalar did appear fairly Gaussian,
occupying a literal semantic previously unoccupied by the other
alternatives.

@@

Using literal semantic data from Experiments 1a, 3a and 4 we conducted
three simulations with our model. Each simulation used the specific
literal semantic data to specify the scale representation available to
our model. The ``entailment'' model used only the original pair of
scalar items pulled from van Tiel (2014). These data were measured in
Experiment 1a. The ``Top two'' model extended the original set of
alternatives with the top two alternatives generated in Experiment 2.
These data were measured in Experiment 3a. The ``Full'' model included
the full set of alternatives, including a neutral valenced alternative.
These data were measured in Experiment 4.

@@

Ignore below this

use a food review paradigm in which `meaning' for a given scalar item
was quantified as a distribution over star-ratings. Quantifying both
literal semantic content and pragmatic judgments as distributions over
stars provides an important interface to our model, especially for
scalar items with ambiguous literal semantics (e.g.~items such as
``liked/loved'' or ``memorable/unforgettable''). In addition to
quantifying literal semantics and pragmatic judgments in Experiments
1a,b and Experiments 3a,b, Experiment 2 used a modified cloze task,
based on van Tiel (2013, Experiment 2???), to generate a set of
plausible alternatives to the scalar items used in Experiments 1a,b. We
extend the set of alternatives measured in Experiments 3a,b and 4 using
data from Experiment 2. Additionally, by looking at the relative
frequencies of alternatives generated in Experiment 2 we were able to
compute a saliency measure for each alternative. Using the literal
semantic data from Experiments 1a, 3a and 4, we modeled pragmatic
enrichment using RSA and compared model predictions to human judgments
obtained in Experiments 1b and 3b. Model performance was significantly
improved with the incorporation of alternatives. This result suggests
that more ``fully specified" scale representations may be active for
human participants while making pragmatic judgments for scalar items.
